### 2022-02-07 manuscript/manuscript.Rmd
Finish the discussion

To visualize the agreement between the pGRF and pLR values measured by the FP and predicted by the models, a series of Bland-Altman plots were built for both the resultant and vetical vectors and for all accelerometer placements. Figure 2 shows the Bland-Altman plots for the pGRF (Panel A) and pLR (Panel B) resultant vector of hip-worn accelerometers. Both plots have shown good agreement levels, as at least `r ba_agreement`\% of the data points are within the limits of agreement and data tended to cluster around zero. Bland-Altman plots for the other accelerometer placements and vectors have shown the same patterns described previously, and can be found in the Supplemental Figure S2. Also, as could be observed by the one-sample *t*-tests results, none of the equations presented a bias different than zero (*p* > 0.05). Furthermore, all of the equations have shown a proportional bias, i.e., the magnitude of the values influence the prediction error. However, as the linear regressions presented a very low R^2^ (maximum value of `r myround(max(ba_regression_ankle_R2), 2)`) this effect is neglectable.

@@

Bone is known to increase its tissue mass and enhance its micro-architecture arrangement in response to mechanical stimulation, particularly at higher magnitudes. This type of high-intensity impact activies have shown to be more associated with bone health improval, even if they are usually performed in low quantities throughout the day. In fact, Vainionpaa et al demonstrated that performing a relatively low number of pACC above 4.9*g* daily is positively associated with increases in bone mineral density. Usually, this acceleration magnitude can only be achieved by explosive (?) movements such as jumps. Nevertheless, accelerometry-based mechanical loading regression models have mostly been validated with a set of activies, such as walking and running, that elict relatively low acceleration magnitudes, usually ranging from X to Y*g*.

@@

Loading rate is a highly sensitive parameter, that is usually calculated by deriving the force from the beggining of the foot contact to the floor to the point where the pGRF is achieved. This is a small time window, usually between X and Y seconds for the jumps that were performed in our protocol, and requires a fine sampling acquisition that captures small graduations on the force values throughout time, which is difficult to achieve with common accelerometer sampling frequecies, that are usually 100Hz at maximum. Based on this and on on results from previous investigations [@Fortune2014; @Veras2020], pLR prediction models are expected to have a lower accuracy compared to the pGRF equations. Nevertheless, although our pLR prediction models had a worse accuracy compared with the pGRF models, its accuracy was similar or even better than the results from previous studies that developed models to predict pLR during walking only [@Fortune2014; @Veras2020].
<!-- TODO: Try and state that this samplling frquency issue is theoretical -->

@@

>>>>

To visualize the agreement between the pGRF and pLR values measured by the FP and predicted by the models, a series of Bland-Altman plots were built for both the resultant and vetical vectors and for all accelerometer placements. Figure 2 shows the Bland-Altman plots for the pGRF (Panel A) and pLR (Panel B) resultant vector of hip-worn accelerometers. Both plots have shown good agreement levels, as at least `r ba_agreement`\% of the data points are within the limits of agreement and data tended to cluster around zero. Bland-Altman plots for the other accelerometer placements and vectors have shown the same patterns described previously, and can be found in the Supplemental Figure S2. Also, as could be observed by the one-sample *t*-tests results, none of the equations presented a bias different than zero (*p* > 0.05). Furthermore, all of the equations have shown a proportional bias, i.e., the magnitude of the values influence the prediction error. However, as the linear regressions presented a very small R^2^ (maximum value of `r myround(max(ba_regression_ankle_R2), 2)`) this effect is neglectable.

@@

Bone is known to increase its tissue mass and enhance its micro-architecture arrangement in response to mechanical stimulation, particularly at higher magnitudes. This type of high-intensity impact activies have shown to be more associated with bone health improval, even if they are usually performed in low quantities throughout the day. In fact, Vainionpää et al demonstrated that performing a relatively low number (<100) of pACC above 4.9*g* daily is positively associated with increases in bone mineral density. Usually, this acceleration magnitude can be achieved mostly by ballistic movements such as jumps. Nevertheless, accelerometry-based mechanical loading regression models have mostly been validated with a set of activies, such as walking and running, that elict relatively low acceleration magnitudes, usually ranging from approximately 1.2 to 6*g* [@Neugebauer2014; @Veras2020].

@@

Loading rate is a highly sensitive parameter, that is usually calculated by deriving the force from the beggining of the foot contact to the floor to the point where the pGRF is achieved. This is a small time window, usually less than 0.2 seconds for the jumps that were performed in our protocol, and requires a fine sampling acquisition that captures small graduations on the force values throughout time, which is difficult to achieve with common accelerometer sampling frequecies, that are usually 100Hz at maximum. Based on this and on on results from previous investigations [@Fortune2014; @Veras2020], pLR prediction models are expected to have a lower accuracy compared to the pGRF equations. Nevertheless, although our pLR prediction models had a worse accuracy compared with the pGRF models, its accuracy was similar or even better than the results from previous studies that developed models to predict pLR during walking only [@Fortune2014; @Veras2020].

@@

Although the models presented in this study showed to be valid, some limitations ought to be considered. First, the choice of activity to elicit high-impact loading was jumping, and several combinations of jump type and height were tested. Nevertheless, the results presented here cannot be assured for other high-impact activities, or even for other types of jump that were not tested. Second, no external sample for model validation was recruited. However, the leave-one-out cross-validation method that was used is the recommended in these situations [@Staudenmayer2012]. Third, to apply these models in accelerometer-recorded free-living physical activity data, there is a need to identify, in the acceleration signal, the periods in which the activity being performed is jumping. Therefore, methods for physical activity pattern detection should be used in combination with these models.

Mechanical loading prediction equations based on accelerometer data have already been proposed for several populations [@Neugebauer2012; @Neugebauer2018; @Veras2020] and using accelerometer in different body placements [@Fortune2014; @Veras2020]. What these past few studies have in common is that they validated their models using locomotion activities, as walking only or walking and runnning. The current study, by setting means to predict mechanical loading in several types and heights of jumps, broadens the application of such models, getting a step closer of the ability to accurately identify daily-living mechanical loading due to physical activity. This ability would allow the monitoring of loading in different contexts and to more fully understand the relationship between mechanical stimulation and its consequent effect on bone health.
